Supplmentary material for "Current status and prospects of R-packages for the design of experiments

### 2022-06-12 paper.Rmd
fixed supp, added renv, added about import for algdesign per dewi's comments

In `r ctv("ExperimentalDesign")` task view, there are `r npkgs` R packages for experimental design and analysis of data from experiments. The sheer quantity and variation of experimental designs in the R-packages are arguably unmatched with any other programming languages, e.g. in Python [@python], only a handful of libraries that generate design of experiment exist (namely `pyDOE`, `pyDOE2`, `dexpy`, `experimenter` and `GPdoemd`) with limited type of designs. Thus, the study of DoE packages, based on quantitative and qualitative data, can give us an objective view to the state of the current experimental designs in practice.

@@

We can see in Figure `r ref("fig:rank-over-time")` that most of the top 10 ranking packages have been in the top 10 for the last 9 years with `lhs` steadily climbing up the ranks in the last few years.

@@

This paper uses the `targets` framework [@targets] for reproducibility, `knitr` [@knitr] and `rmarkdown` [@rmarkdown] for creating reproducible documents, `ggplot2` [@ggplot2], `ggraph` [@ggraph], `ggwordcloud` [@ggwordcloud] and `colorspace` [@colorspace] for visualisation, `kableExtra` [@kableExtra] for customising the table in the Supplementary Material and `tidyverse` [@Wickham2019-mj], `tidytext` [@tidytext], `pluralize` [@pluralize], and `ineq` [@ineq] for data processing and manipulation, and `cranlogs` [@cranlogs] and `ctv` [@ctv] for extracting data. All code to reproduce this paper is found at `r url("https://github.com/emitanaka/paper-DoE-review")`.

>>>>

In `r ctv("ExperimentalDesign")` task view, there are `r npkgs` R packages for experimental design and analysis of data from experiments. The sheer quantity and variation of experimental designs in the R-packages are arguably unmatched with any other programming languages, e.g. in Python [@python], only a handful of packages that generate design of experiment exist (namely `pyDOE`, `pyDOE2`, `dexpy`, `experimenter` and `GPdoemd`) with limited type of designs. Thus, the study of DoE packages, based on quantitative and qualitative data, can give us an objective view to the state of the current experimental designs in practice.

@@

We can see in Figure `r ref("fig:rank-over-time")` that most of the top 10 ranking packages have been in the top 10 for the last 9 years with `lhs` steadily climbing up the ranks in the last few years. It should be noted that the download of one package can prompt a download of another package; the most notable dependency network is `AlgDesign` and `agricolae`, where the former is an import for the latter. The full dependency network within the DoE packages is shown later in Figure \@ref(fig:plot-doe-network).

@@

This paper uses the `targets` framework [@targets] and `renv` [@renv] for reproducibility, `knitr` [@knitr] and `rmarkdown` [@rmarkdown] for creating reproducible documents, `ggplot2` [@ggplot2], `ggraph` [@ggraph], `ggwordcloud` [@ggwordcloud] and `colorspace` [@colorspace] for visualisation, `kableExtra` [@kableExtra] for customising the table in the Supplementary Material and `tidyverse` [@Wickham2019-mj], `tidytext` [@tidytext], `pluralize` [@pluralize], and `ineq` [@ineq] for data processing and manipulation, and `cranlogs` [@cranlogs] and `ctv` [@ctv] for extracting data. All code to reproduce this paper is found at `r url("https://github.com/emitanaka/paper-DoE-review")`.

### 2022-06-12 paper/arxiv/arxiv.tex
fixed supp, added renv, added about import for algdesign per dewi's comments

In
\href{http://CRAN.R-project.org/view=ExperimentalDesign}{\emph{ExperimentalDesign}}
task view, there are 114 R packages for experimental design and analysis
of data from experiments. The sheer quantity and variation of
experimental designs in the R-packages are arguably unmatched with any
other programming languages, e.g.~in Python (Rossum 1995), only a
handful of libraries that generate design of experiment exist (namely
\texttt{pyDOE}, \texttt{pyDOE2}, \texttt{dexpy}, \texttt{experimenter}
and \texttt{GPdoemd}) with limited type of designs. Thus, the study of
DoE packages, based on quantitative and qualitative data, can give us an
objective view to the state of the current experimental designs in
practice.

@@

We can see in Figure \ref{fig:rank-over-time} that most of the top 10
ranking packages have been in the top 10 for the last 9 years with
\texttt{lhs} steadily climbing up the ranks in the last few years.

>>>>

In
\href{http://CRAN.R-project.org/view=ExperimentalDesign}{\emph{ExperimentalDesign}}
task view, there are 114 R packages for experimental design and analysis
of data from experiments. The sheer quantity and variation of
experimental designs in the R-packages are arguably unmatched with any
other programming languages, e.g.~in Python (Rossum 1995), only a
handful of packages that generate design of experiment exist (namely
\texttt{pyDOE}, \texttt{pyDOE2}, \texttt{dexpy}, \texttt{experimenter}
and \texttt{GPdoemd}) with limited type of designs. Thus, the study of
DoE packages, based on quantitative and qualitative data, can give us an
objective view to the state of the current experimental designs in
practice.

@@

We can see in Figure \ref{fig:rank-over-time} that most of the top 10
ranking packages have been in the top 10 for the last 9 years with
\texttt{lhs} steadily climbing up the ranks in the last few years. It
should be noted that the download of one package can prompt a download
of another package; the most notable dependency network is
\texttt{AlgDesign} and \texttt{agricolae}, where the former is an import
for the latter. The full dependency network within the DoE packages is
shown later in Figure @ref(fig:plot-doe-network).

### 2022-06-12 supp.Rmd
fixed supp, added renv, added about import for algdesign per dewi's comments

---
title: Supplmentary material for "Current status and prospects of R-packages for the design of experiments"
author:
  - Emi Tanaka
  - Dewi Amaliah 
bibliography: paper.bib
keywords: ["experimental design", "CRAN task view", "user interface"]
output: 
  bookdown::pdf_document2
header-includes:
  - \renewcommand{\figurename}{Figure S}
  - \makeatletter
  - \def\fnum@figure{\figurename\thefigure}
  - \makeatother
---

```{css, echo = FALSE}
h1, h2, h3, div > * {
 font-family: "Helvetica Neue",Helvetica,Arial,sans-serif;
}

@@

tar_load(npkgs)
tar_load(gini_yearly)
tar_load(gini_yearly_ctv)
```

@@

```{r ctv-summ-table}
tar_read(ctv_summary_table) %>% 
  knitr::kable(col.names = c("Name", "Topic", "# of packages", "Total # of contributors" , "Average # of contributors", "Intra-connectivity (%)"), 
               caption = "A summary table for the CRAN task view that shows in order: the name of the task view, the full topic name, the total of packages, the total number of contributors, the average number of contributors, and the intra-connectivity. The intra-connectivity measures the percentage of packages that depends, suggest or imports at least one other package within the same task view. A low intra-connectivity suggests that development within the topic mostly occur in silos whilst high  intra-connectivity suggests that there are more interactions within the topic. The row is ordered by the average number of contributors.",
               digits = c(0, 0, 0, 1, 2, 0),
               booktabs = TRUE ) %>%
 kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>% 
 kableExtra::column_spec(2, width = "12em") %>% 
 kableExtra::column_spec(3:6, width = "5em")

@@

>>>>

---
title: Supplmentary material for "Current status and prospects of R-packages for the design of experiments"
author:
  - Emi Tanaka
  - Dewi Amaliah 
bibliography: pkgs.bib
keywords: ["experimental design", "CRAN task view", "user interface"]
output: 
  bookdown::pdf_document2:
    toc: false
    keep_tex: true
    citation_package: biblatex
header-includes: |
  \usepackage{colortbl}
  \usepackage{bera}
  \usepackage{xcolor}
  \usepackage{hyperref}
  \usepackage{booktabs}
  \usepackage[utf8]{inputenc}
  \usepackage{caption}
  \renewcommand{\figurename}{Figure S}
  \makeatletter
  \def\fnum@figure{\figurename\thefigure}
  \makeatother
  \renewcommand{\tablename}{Table S}
  \makeatletter
  \def\fnum@table{\tablename\thetable}
  \makeatother

  \usepackage{bera}
---

@@

tar_load(npkgs)
tar_load(gini_yearly)
tar_load(gini_yearly_ctv)

#renvLock <- jsonlite::read_json("renv.lock")
#sink("pkgs.bib")
#knitr::write_bib(names(renvLock$Packages))
#sink()
```

@@

```{r ctv-summ-table}
tar_read(ctv_summary_table) %>% 
  knitr::kable(col.names = c("Name", "Topic", "# of packages", "Total # of contributors" , "Average # of contributors", "Intra-connectivity (%)"), 
               caption = "A summary table for the CRAN task view that shows in order: the name of the task view, the full topic name, the total of packages, the total number of contributors, the average number of contributors, and the intra-connectivity. The intra-connectivity measures the percentage of packages that depends, suggest or imports at least one other package within the same task view. A low intra-connectivity suggests that development within the topic mostly occur in silos whilst high  intra-connectivity suggests that there are more interactions within the topic. The row is ordered by the average number of contributors.",
               digits = c(0, 0, 0, 1, 2, 0),
               booktabs = TRUE,
               longtable = TRUE) %>%
 kableExtra::kable_styling(latex_options = c("striped", "scale_down", "repeat_header"),
                           repeat_header_continued = "\\textit{(Continued on next page...)}") %>% 
 kableExtra::column_spec(2, width = "12em") %>% 
 kableExtra::column_spec(3:6, width = "5em")

@@

# Session information {-}

```{r session-info, echo = FALSE}
renv_lock <- jsonlite::read_json("renv.lock")
pander::pander(sessionInfo(package = names(renv_lock$Packages)), compact = FALSE)
```
